---
output: pdf_document
---
## Workflow Spec Report

```{r, echo=FALSE, warning=FALSE,results='hide',message=FALSE}
connection_name <- "KyleODBC"
user <- "reports"
password <- "EWQ321#@!"

library(pander)
library(RODBC)

channel <- odbcConnect(connection_name,
                       uid=user,
                       pwd=password,
                       rows_at_time = 1)

sqlQuery(channel, "USE support_finance")
```


1. Workflow should have less than 500 instances in progress
    - Test:
```sql
SELECT count(*) 
FROM wf_instance 
WHERE wf_status in ('I', 'R', 'A', 'P')
```
    - Expectation: test < 500


```{r, echo=FALSE}
spec1 <- sqlQuery(channel,"
SELECT count(*) 
FROM wf_instance 
WHERE wf_status in ('I', 'R', 'A', 'P')
")

result <- "FAILED"
result_color <- "pink"
if (spec1 < 500) {
  result <- "PASS"
  result_color <- "lightgreen"
}
```

    - <span style="background-color:`r result_color`">
    Result: `r result` ; test = `r spec1`
    </span>


2. Workflow should have no instances in progress that where started before one year ago
    - Test:
```sql
SELECT count(*) 
FROM wf_instance 
WHERE wf_start <= DATEADD(year, -1, GETDATE())
and wf_status in ('I', 'R', 'A', 'P')
```
    - Expectation: test = 0 


```{r, echo=FALSE}
spec2 <- sqlQuery(channel,"
SELECT count(*) 
FROM wf_instance 
WHERE wf_start <= DATEADD(year, -1, GETDATE()) 
and wf_status in ('I', 'R', 'A', 'P')
")

result <- "FAILED"
result_color <- "pink"
if (spec2 == 0 ) {
  result <- "PASS"
  result_color <- "lightgreen"
}
```

    - <span style="background-color:`r result_color`">
    Result: `r result` ; test = `r spec2`
    </span>



3. Workflow should have no in progress instances on inactive models
    - Test:
```sql
SELECT count(t2.unique_key)
FROM
    (SELECT wf_model_id, wf_version FROM wf_model WHERE wf_status <> 'A') AS t1
    INNER JOIN
    (SELECT * FROM wf_instance WHERE wf_status in ('I', 'R', 'A', 'P')) AS  t2
    ON t1.wf_model_id = t2.wf_model_id
WHERE t1.wf_version = t2.wf_version
```
    - Expectation: test = 0


```{r, echo=FALSE}
spec3 <- sqlQuery(channel,"
SELECT count(t2.unique_key)
FROM
    (SELECT wf_model_id, wf_version FROM wf_model WHERE wf_status <> 'A') AS t1
    INNER JOIN
    (SELECT * FROM wf_instance WHERE wf_status in ('I', 'R', 'A', 'P')) AS  t2
    ON t1.wf_model_id = t2.wf_model_id
WHERE t1.wf_version = t2.wf_version
")

result <- "FAILED"
result_color <- "pink"
if (spec3 == 0) {
  result <- "PASS"
  result_color <- "lightgreen"
}
```

    - <span style="background-color:`r result_color`">
    Result: `r result` ; test = `r spec3`
    </span>



4. Workflow instances in progress should have at least one pending history record
    - Test:
```sql
SELECT count(*)
FROM wf_instance
WHERE wf_status = 'I'
AND wf_key NOT IN (
    SELECT DISTINCT wf_key
    FROM wf_history
    WHERE wf_status = 'P'
)
```
    - Expectation: test = 0


```{r, echo=FALSE}
spec4 <- sqlQuery(channel,"
SELECT count(*)
FROM wf_instance
WHERE wf_status = 'I'
AND wf_key NOT IN (
    SELECT DISTINCT wf_key
    FROM wf_history
    WHERE wf_status = 'P'
)
")

result <- "FAILED"
result_color <- "pink"
if (spec4 == 0) {
  result <- "PASS"
  result_color <- "lightgreen"
}
```

    - <span style="background-color:`r result_color`">
    Result: `r result` ; test = `r spec4`
    </span>



5. Workflow Users should be enabled using 'Y' and not 'W'
    - Test:
```sql
select count(*)
from us_usno_mstr
where us_wf_enable like '%W%'
```
    - Expectation: test = 0


```{r, echo=FALSE}
spec5 <- sqlQuery(channel,"
select count(*)
from us_usno_mstr
where us_wf_enable like '%W%'
")

result <- "FAILED"
result_color <- "pink"
if (spec5 == 0) {
  result <- "PASS"
  result_color <- "lightgreen"
}
```

    - <span style="background-color:`r result_color`">
    Result: `r result` ; test = `r spec5`
    </span>



6. Users should have a default GL ledger
    - Test:
```sql
SELECT DISTINCT us_misc_flags11
FROM us_usno_mstr
```
    - Expectation: test should not have null or blank value


```{r, echo=FALSE}
spec6 <- sqlQuery(channel,"
SELECT DISTINCT us_misc_flags11
FROM us_usno_mstr
")

result <- "PASS"
result_color <- "lightgreen"

if (any(is.na(spec6$us_misc_flags11)) == TRUE) {
  result <- "FAILED"
  result_color <- "pink"
}


if (any(grep("[[:blank:]]",spec6$us_misc_flags11)) == TRUE) {
  result <- "FAILED"
  result_color <- "pink"
}

```

    - <span style="background-color:`r result_color`">
    Result: `r result` ; test found: 
        ```{r, echo=FALSE} 
        spec6
        ```
    </span>



7. Users should have a default JL ledger
    - Test:
```sql
SELECT DISTINCT us_misc_flags12
FROM us_usno_mstr
```
    - Expectation: test should not have nullor blank value


```{r, echo=FALSE}
spec7 <- sqlQuery(channel,"
SELECT DISTINCT us_misc_flags12
FROM us_usno_mstr
")

result <- "PASS"
result_color <- "lightgreen"

if (any(is.na(spec7$us_misc_flags12)) == TRUE) {
  result <- "FAILED"
  result_color <- "pink"
}


if (any(grep("[[:blank:]]",spec7$us_misc_flags12)) == TRUE) {
  result <- "FAILED"
  result_color <- "pink"
}

```

    - <span style="background-color:`r result_color`">
    Result: `r result` ; test found: 
        ```{r, echo=FALSE} 
        spec7
        ```
    </span>

8. There should only be one distinct workflow engine, 'NONE', and/or null.
    - Test:
```sql
SELECT DISTINCT wf_engine
FROM wf_instance
WHERE wf_status IN ('I', 'R', 'A', 'P')
```
    - Expectation: test should only return one row with a server address


```{r, echo=FALSE}
spec8 <- sqlQuery(channel,"
SELECT DISTINCT wf_engine
FROM wf_instance
WHERE wf_status IN ('I', 'R', 'A', 'P')
")

result <- "PASS"
result_color <- "lightgreen"

row_count <- grep("[A-Za-z0-9]", spec8$wf_engine, value=TRUE)
row_count <- subset(row_count, !grepl( "^NONE", row_count), drop = TRUE )
row_count <- NROW(row_count)

if (row_count > 1) {
  result <- "FAILED"
  result_color <- "pink"
}

```

    - <span style="background-color:`r result_color`">
    Result: `r result` ; test found: 
        ```{r, echo=FALSE}
        spec8
        ```
    </span>

### Analytics
#### Overall Active Instances
```{r, echo=FALSE, warning=FALSE}
overall <- sqlQuery(channel,"
SELECT wf_model_id as Model, wf_status as Status, wf_start
FROM wf_instance
WHERE wf_status in ('I', 'R', 'A', 'P')
")

library(ggplot2)
ggplot(overall, aes(factor(Model),fill=Status)) + geom_bar() + coord_flip()
```


#### Summary of Active instances
```{r, echo=FALSE}
df1 <- sqlQuery(channel,"
SELECT wf_status, wf_start, wf_model_id
FROM wf_instance
WHERE wf_status in ('I', 'R', 'A', 'P')
")

summary(df1)

```


#### Active Instance Count Across the Years
```{r xtable, echo=FALSE, results="asis"}
df2 <- sqlQuery(channel,"
SELECT
    wf_model_id AS Model,
    wf_status AS Status,
    Count(
        CASE
            WHEN wf_start >= '2016-01-01' AND wf_start < '2017-01-01'
                THEN wf_start
            ELSE NULL
        end
    ) AS '2016',
    Count(
        CASE
            WHEN wf_start >= '2015-01-01' AND wf_start < '2016-01-01'
                THEN wf_start
            ELSE NULL
        end
    ) AS '2015',
    Count(
        CASE
            WHEN wf_start < '2015-01-01'
                THEN wf_start
            ELSE NULL
        end
    ) AS '2014 and later',
    Count(wf_start) AS Total
FROM   wf_instance
WHERE  wf_status IN ('I', 'R', 'A', 'P')
GROUP BY wf_model_id, wf_status
ORDER BY wf_model_id, wf_status DESC;
")

print(pandoc.table(df2), type="html", include.rownames = F)
```




```{r, echo=FALSE}
odbcClose(channel)
```
